(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2015-04-23 ms/ms.Rnw
Pushing from linux

  # The path to the ms directory may need to be changed for different users
  # Manuscript files
  pathMS <- "~/Google Drive/CardLocalAdaptation/ms"

@@

<<focClim, echo = FALSE>>=
# Read in climate data for 16 focal populations to use in making Table 1
load('~/Google Drive/CardLocalAdaptation/Data/Climate/Robjects/focClim.RData') # focClim

>>>>

  # The path to the ms directory may need to be changed for different users
  # Manuscript files
  pathMS <- "~/Google Drive/CardLocalAdaptation/ms" # Chris' MacBook
  pathMS <- "~/Documents/CardAdapt/ms" # Chris' Linux laptop

@@

<<focClim, echo = FALSE>>=
# Read in climate data for 16 focal populations to use in making Table 1
# need to make this available from ms directory
load('~/Google Drive/CardLocalAdaptation/Data/Climate/Robjects/focClim.RData') # focClim
